Analyse gender in music psychology from journal publication data

### 2025-09-12 manuscript/manuscript.qmd
added eminent author idea, revised figure 3 (merged two plots)

```{r}
#| id: countrywise
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| output: asis
#| fig-width: 9
#| fig-height: 6
#| fig.cap: > 
#|   Female author odds ratio across the prolific countries publishing music psychology (with more than sixty publications).

@@

- If we want to add the continents at this figure, that's possible.

>>>>

```{r}
#| id: countrywise
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| output: asis
#| fig-width: 9
#| fig-height: 8
#| fig.cap: > 
#|   Female author odds ratio across the prolific countries publishing music psychology (with more than sixty publications).

@@
